\documentclass[letterpaper,11pt]{article}

\usepackage{nccmath}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
    \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
    \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


%text -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\vspace{-5pt}

\begin{center}
    \textbf{\Huge \scshape Alastair Hamilton} \\
    \textit{\small +44 0770 775 1450 $|$ alastair.amhamilton@icloud.com $|$ Dual British-Irish Citizenship}
    \vspace{8pt} 
\end{center}

% -------------------- SUMMARY --------------------
\section{Summary}
\begin{itemize}[leftmargin=0.2in, label={}]
    \item 
        \begin{minipage}[t]{1.0\linewidth}
            I am a creative, hardworking and self-driven professional with
            nearly a decade of experience in the data science and machine
            learning space, working in finance, risk, cybersecurity and
            sustainability. Over the past two years I have successfully
            built a robust data science function from the ground up at a
            successful start-up but am now looking to make a significant
            shift into the gaming industry and embrace a new challenge where
            I follow my heart and leap into the unknown, pursuing my dream in
            becoming a game developer.

            In my spare time I enjoy playing my piano, gaming and whatever 
            niche hobby I have at the time.
        \end{minipage}
\end{itemize}

% -------------------- TECH STACK -------------------
\section{Tech Stack}
\begin{itemize}[leftmargin=0.2in, label={}]
    \item 
        \begin{minipage}[t]{1.0\linewidth}
            \begin{tabbing}
            \textbf{Languages:}  \=Python, SQL, Terraform, Bash \\
            \textbf{Cloud:}\>AWS, GCP, Azure, Sagemaker, VertexAI, 
            Azure Machine Learning \\
            \textbf{Packages:}\>pandas, NumPy, scikit-learn, Transformers,
            PyTorch, matplotlib, nltk, LangChain \\
            \textbf{Ops:}\>MLflow, Weights and Biases, Github, 
            Github Actions
            \end{tabbing} 
        \end{minipage}
\end{itemize}


% -------------------- EDUCATION --------------------
\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{University of Edinburgh} & June 2017 \\
        \textit{\small BSc Theoretical Physics} & \textit{\small 2:1 (69\%)} \\
    \end{tabular*}
\end{itemize}


% -------------------- WORK EXPERIENCE --------------------
\section{Employment}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item
    \begin{minipage}[t]{0.75\linewidth}
        \textbf{Altruistiq} $|$ Sustainability \\
    \end{minipage} \hfill \textit{\small May 2022 -- Present} \\
    \vspace{-7pt}
        \textit{\small Lead Data Scientist $\rightarrow$ Senior Lead Data Scientist}
    \vspace{-7pt}
    \begin{itemize}[label={\tiny\textbullet}]
        \item
        \begin{minipage}[t]{0.75\linewidth}
            \item\small 
                Created a pipeline to automate our tagging process for 
                incoming customer data using
                a custom search algorithm combining BM25 ranking,
                vector search, cross-encoder reranking and cluster-based
                reordering, where the embedding and cross-encoder models were
                fine-tuned SOTA LLMs hosted on GPU infrastructure. The algorithm 
                had a top-1 accuracy of 11\% and a top-30 accuracy of 34\%,
                enabling our tagging process to become a review process, 
                generating revenue through boosts in productivity.
            \item\small 
                Semi-automated our PDF data extraction using a pipeline 
                of models for clustering, grouping, multi-label multi-class 
                classification and text extraction, with human-in-the-loop
                to safely deal with any corrections. The full process had a
                baseline KPI of $\sim$50\% accuracy and removed the need for technical
                engineers, saving the business $\sim$£172,000/year.
            \item\small
                Coded all models, MLOps, DevOps, infrastructure and 
                internal tooling for my team. This includes our MLOps architecture
                for model versioning, model release, data versioning, data 
                pipelining, and model monitoring.
            \item\small
                Worked with product managers to break down complex data science
                and ML project requirements into a clear backlog that could
                be managed in sprint cycles by non-technical managers
                and be prioritised against other ongoing company projects.
            \end{minipage}
    \end{itemize}

    \vspace{0.2cm}

    \item
    \begin{minipage}[t]{0.75\linewidth}
        \textbf{Lloyds Banking Group} $|$ Financial Services \\
    \end{minipage} \hfill \textit{\small Sep 2018 -- May 2022} \\
    \vspace{-7pt}
    \textit{\small Cognitive Data Science Manager $\rightarrow$ Data Scientist}
    \vspace{-7pt}
    \begin{itemize}[label={\tiny\textbullet}]
        \item
            \begin{minipage}[t]{0.75\linewidth}
                \item\small
                    Developed a vector-based retrieval search engine as a
                    replacement for an FAQ Risk chatbot, avoiding 
                    $\sim$£300k in costs.
                \item\small
                    Developed and embedded a topic modelling tool using 
                    unsupervised LDA topic models for identifying emerging 
                    themes in customer vulnerability documents, resulting in 
                    the successful identification of OOS climate change risks.
                \item\small
                    Developed a novelty detection algorithm using the CluStream 
                    framework as part of the bank's insider criminal threat 
                    detection project.
                \item\small
                    Authored and supported a Data Science Masters project at the 
                    University of Edinburgh, focusing on utilising Bayesian 
                    Neural Networks for anomaly detection.
            \end{minipage}
    \end{itemize}

    \vspace{0.2cm}

\end{itemize}

\section{Employment \textit{(Continued)}}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item
    \begin{minipage}[t]{0.75\linewidth}
        \textbf{BP} $|$ Oil \& Gas \\
    \end{minipage} \hfill \textit{\small Sep 2017 -- Jun 2018} \\
    \vspace{-7pt}
    \textit{\small Supply and Trading Market Intelligence Analyst (Graduate)}
    \vspace{-7pt}\vspace{0.2cm}
\end{itemize}
% -------------------- PUBLICATIONS --------------------

\section{Publications}
\begin{itemize}[leftmargin=0.2in, label={}]
    \item 
        \begin{minipage}[t]{0.75\linewidth}
            Thompson, S., Teixeira-Dias, F., Paulino, M., \& Hamilton, A. \\
            \textit{Predictions on multi-class terminal ballistics datasets using conditional Generative Adversarial Networks.} \\
            Neural Networks, 154, 425-440.
        \end{minipage} \hfill \textit{2022}
\end{itemize}

\begin{itemize}[leftmargin=0.2in, label={}]
  \item
      \begin{minipage}[t]{0.75\linewidth}
          Thompson, S., Teixeira-Dias, F., Paulino, M., \& Hamilton, A. \\
          \textit{Ballistic response of armour plates using Generative Adversarial Networks.} \\
          Defence Technology, 18(9), 1513-1522.
      \end{minipage} \hfill \textit{2022}
\end{itemize}


\end{document}

